Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
rewrite 3 points

As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}. The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients. In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
%
\begin{equation} \textstyle
  \valpha_{\vu}  =  \sum_{i=1}^N  \vkzi \, \hat{\alpha}_{i}
  \quad \text{and} \quad
  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
%
where the sparse dual variables are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$. Using this sparse definition of the dual variables, our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}
   \quad \text{and} \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$, instead of the full data set $\dataset$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplace} and a kernel function $\kappa$ . Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.  Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.

@@

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .\
%
We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$. Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$. Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

@@

% We start by obtaining a posterior over the weights of a trained neural network via the Laplace approximation.
% We then show how we can obtain a function-space posterior, (i.e. a GP posterior)
% by linearising the neural network around the weights Maximum a Posteriori (MAP) estimate.
% We then show that by linearising the neural network we can obtain a function-space posterior, i.e. a GP posterior.
% We paraterise our single-step dynamic model $\transitionFnWithParams : \inputDomain \rightarrow \outputDomain$
% as an $L\text{-layer}$ NN with weights $\weights$.

%A Gaussian process (GP) is a distribution over real-valued functions $f(\cdot): \mathcal{X} \rightarrow \R$ defined over $\mathcal{X}$.
%Formally, a GP is defined as,
%\begin{align}
%\label{eq-gp-prior}
%  f(\cdot) \sim \mathcal{N}\left( \mu(\cdot), k(\cdot,\cdot') \right) \quad
%  \mu(\cdot): \mathcal{X} \rightarrow \R \quad
%  k(\cdot,\cdot'): \mathcal{X} \times \mathcal{X} \rightarrow \R
%\end{align}
%where $\mu(\cdot)$ denotes a mean function and $k(\cdot,\cdot')$ a positive definite covariance function, also known as a kernel.
%Given a data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
%we can obtain the GP posterior via multivariate normal conditioning,
%\begin{align}
%\label{eq-gp-predictive-posterior}
%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} (\mathbf{y} - \bm\mu_{\mathbf{X}})),
%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
%\end{align}
%% Our GP posterior is then given by,
%\todo{add mean func to GP posterior if we're using one}
%\begin{align}
%\label{eq-gp-predictive-posterior}
%  p(f(\mathbf{x}_{*}) \mid \mathbf{y}) &= \mathcal{N}
%  % \left( f(\mathbf{x}_{*}) \mid \mathbf{A} \mathbf{m}^{*}, \mathbf{A}\mathbf{K}_{\mathbf{x}\mathbf{x}}^{-1} \mathbf{A}^{T} \right) \\
%  \left( f(\mathbf{x}_{*}) \mid \mu(\mathbf{x}_{*}) + \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}} \mu_{\mathbf{x}},
%  k_{**} - \mathbf{k}_{*\mathbf{x}} \left(\mathbf{K}_{\mathbf{x}\mathbf{x}} + \bm\Lambda(\mathbf{y} ; \mathbf{f})^{-1} \right)^{-1} \mathbf{k}_{*\mathbf{x}}^{T} \right)
%\end{align}
%where $\bm\Lambda(\mathbf{y} ; \mathbf{f}) = \nabla^{2}_{\mathbf{f} \mathbf{f}} \log p(\mathbf{y} \mid \mathbf{f})$ can be viewed as per-input noise. \todo{I'm unsure about this per input noise bit. Check with paul.}
%\todo{what about regression/classification likelhoods}
%This GP predictive posterior is computationally expensive as it requires inverting an $N\times N$ matrix.
%\textbf{Sparse Gaussian processes}
%% The GP predictive posterior in \cref{eq-gp-predictive-posterior} is computationally expensive as it requires inverting an $N\times N$ matrix.
%A practical and computationally appealing alternative is to augment the joint probability space with pseudo inputs $\mathbf{Z} \in \R^{M \times D}$
%and corresponding outputs
%$\mathbf{u} = f(\mathbf{Z}; \weights) \in \R^{M \times C}$, known as inducing variables, where $M \ll N$.
%\todo{cite sparse gp papers}
%Instead of collapsing the inducing variables like \cite{titsiasVariational2009}, they can be treated variationally
%$p(\mathbf{u} \mid \mathbf{y}) \approx q(\mathbf{u}) = \mathcal{N}\left( \mathbf{u} \mid \mathbf{m}, \mathbf{V} \right)$, where $\mathbf{m}$ and $\mathbf{V}$ are variational parameters
%which need to be optimised \citep{hensmanGaussian2013}.
%The sparse variational GP (SVGP) predictive posterior is then given by,
%\begin{align}
%\label{eq-dual-svgp-predictive-posterior}
%  p(f(\mathbf{x}_{*}) \mid \mathbf{y})
%&\approx \mathcal{N} \left( f(\mathbf{x}_{*}) \mid \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{m}^{*},
%  k_{**} - \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
%  % \mathbf{k}_{*\inducingInput} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\inducingInput}^{T}
%  + \mathbf{k}_{*\mathbf{z}} \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}}  \mathbf{V}^{*}  \mathbf{K}^{-1}_{\mathbf{z}\mathbf{z}} \mathbf{k}_{*\mathbf{z}}^{T}
%  \right)
%\coloneqq q_{\inducingVariable}(f(\mathbf{x}_{*}))
%\end{align}
%\textbf{Deep learning}
%Given the data set $\dataset = \{\mathbf{x}_{n} \in \inputDomain, \mathbf{y}_{n} \in \outputDomain\}_{n=0}^{N}$,
%the goal of (supervised) deep learning, is to train the weights $\weights \in \R^{P}$ of an $L\text{-layer}$ NN
%$f : \inputDomain \rightarrow \outputDomain$ to minimize the (regularized) empirical risk,
%\begin{align} \label{eq-empirical-risk}
%  \weights^{*} = \arg \min_{\weights \in \R^{D}} \mathcal{L}(\dataset;\weights) = \arg \min_{\weights \in \R^{D}} \left(
%  \sum_{n=0}^{N-1} l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) + R(\weights)  \right).
%\end{align}
%In practice, it is common to use the mean squared error (MSE) loss
%$l(f(\mathbf{x}_{n} ; \weights),\mathbf{y}_{n}) = \|f(\mathbf{x}_{n} ; \weights) - \mathbf{y}_{n} \|^{2}_{2}$
%and to use the weight decay regularizer $R(\weights)=\frac{1}{2}\gamma^{-2}\|\weights\|^{2}_{2}$.
%However, the practioner is free to choose any loss and regularizer. \todo{I think?}
%% \textbf{Bayesian neural networks}
%% \textbf{Weight space to function space}
%From a Bayesian perspective, we can interpret the terms in \cref{eq-empirical-risk} as the log-prior and the i.i.d. log likelihood, i.e.,
%\begin{align} \label{eq-log-prior}
%  R(\weights) &= \underbrace{\log p(\weights)}_{\text{log prior}} = \log \mathcal{N}(\weights \mid 0, \gamma^{2} \mathbf{I}) \\
%  l(f(\mathbf{x}_{n} ; \weights), \mathbf{y}_{n}) &= \underbrace{\log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights))}_{\text{log likelihood}}
%  = \log \mathcal{N} \left( \mathbf{y}_{n} \mid f(\mathbf{x}_{n}; \weights), \mathbf{I} \right) \label{eq-log-likelihood}
%\end{align}
%\textbf{NN to GP}
%Given this interpretation, we can represent the weight space prior from \cref{eq-log-prior}, in
%function space, by linearising the BNN around $\weights^{*}$ and interpretting it as a GP.
%The GP prior is then given by,
%\begin{align} \label{eq-laplace-approx-function-space}
%  % \transitionFn_{\weights_{i}}(\cdot) \sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \qquad
%  f(\cdot ;\weights) \sim \mathcal{N} \left( \mu(\cdot), k(\cdot, \cdot') \right) \quad
%  % \mu_{\weights_{i}^{*}}(\cdot)
%  \mu(\cdot)
%  = 0 \quad
%  % = f(\cdot ;\weights^{*}) \quad
%  % K_{\weights_{i}^{*}}(\cdot, \cdot')
%  k(\cdot, \cdot')
%  = \frac{1}{\gamma^{2}} \mathbf{J}(\cdot) \mathbf{J}(\cdot')^{T},
%\end{align}
%where the kernel is the neural tangent kernel (NTK) \citep{immerImprovingPredictionsBayesian2021},
%\todo{what mean function shoudl this use???}
%\todo{NTK times some factor??}
%with Jacobian given by $\mathbf{J}(\cdot) = \odv{\transitionFn(\cdot; \weights)}{\weights}_{\weights=\weights^{*}}$.
%% The kernel in \cref{eq-laplace-approx-function-space} is the neural tangent kernel (NTK)
%% $k(\mathbf{x}, \mathbf{x}') = \sigma_{0}^{2} J_{\weights^{*}}(\mathbf{x}) J_{\weights^{*}}(\mathbf{x}')^{T}$
%% \citep{immerImprovingPredictionsBayesian2021}
%% to formulate the GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$.
%Given this GP prior, we can use \cref{eq-gp-predictive-posterior} to obtain our GP posterior by conditioning on the data.
%% Given our GP prior, we can use the properties of multivariate normals to obtain our GP posterior by conditioning on the data.
%% where $\mathbf{A} = \mathbf{k}_{*\mathbf{x}} \mathbf{K}^{-1}_{\mathbf{x}\mathbf{x}}$
%In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
%Intuitively, we can view the optimisation in \cref{eq-empirical-risk} as learning our kernel.
%As a result, our NTK may be highly non stationary as it is dependent on the NN architecture, for example, the activation functions.
%It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
%so the function space prior (and thus posterior) is only a locally linear approximation.
%We now have a method to obtain a GP posterior from a trained DNN.
%% In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior obtained from the Laplace approximation.
%In contrast to other approaches, our formulation has not restricted us to using a weight-space posterior from a BNN.
%However, in practice, the GP posterior is not very useful as it requires inverting an $N\times N$ matrix which has complexity $\mathcal{O}(N^{3})$.
%The SVGP in \cref{eq-dual-svgp-predictive-posterior} offers a solution to this problem but it is not immediately clear how to set $\mathbf{m}$ and $\mathbf{V}$.
%In the next section, we show how we can directly obtain an SVGP posterior (i.e. set $\mathbf{m}$ and $\mathbf{V}$) directly from both
%1) a trained NN and 2) a BNN weight-space posterior.
%% $\mathbf{m}$ and $\mathbf{V}$
%% However, it is not obvious how we can use a SVGP to set $\mathbf{m}$ and $\mathbf{V}$
%% In contrast, to previous work, this approach did not require us Laplace approximation. we will not restrict our
%% It is worth noting that the NTK linearises the network around the optimised parameters $\weights^{*}$,
%% so the function space prior (and thus posterior) is only a locally linear approximation.
%% In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
%% It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
%\section{Methods}
%In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.
%We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space.
%However, we consider the variational formulation introduced by \cite{adamDualParameterizationSparse2021}, where the optimal variational parameters are given by,
%\begin{align} \label{eq-dual-params}
%\mathbf{m}^{*} = \mathbf{V}^{*}\bm\alpha^{*} \quad \mathbf{V}^{*} = [\mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} + \bm\beta^{*}]
%\end{align}
%Importantly, we can calculate the natural parameters $(\bm\alpha, \bm\beta)$ in closed form,
%\todo{paul needs to update \cref{eq-dual-svgp-params}}
%\begin{align} \label{eq-dual-svgp-params}
%\bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
%\bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right].
%\end{align}
%This simplifies SVGP inference \citep{hensmanGaussian2013} as it no longer requires the variational parameters $(\mathbf{m}, \mathbf{V})$ to be optimised.
%% Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
%% conditioning on new observations reduces to suming the dual variables from the previous time
%% step with an update, given by,
%% \todo{pick best way to show new data (using superscript new or just time indexing?)}
%% \begin{align} \label{eq-dual-update-svgp}
%% \bm\alpha_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right] \\
%% \bm\beta_{n} &=  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(f(\mathbf{x}_{n}))} \left[ \log p(\mathbf{y}_{n} \mid f(\mathbf{x}_{n}) ) \right]
%% \end{align}
%% We follow \cite{csatoSparseOnlineGaussian2002} and express our GP posterior in the dual parameter space,
%% % to write GP posterior $p(f(\mathbf{X} ;\weights_{0:i}) \mid \dataset_{0:i})$ as,
%% \begin{align} \label{eq-gp-post}
%%   \mathbb{E}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
%%   \mathbb{V}_{p(f(\mathbf{x}_{*}) \mid \mathbf{y}_{n})} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \text{diag}(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
%% \end{align}
%% % \begin{align} \label{eq-laplace-approx-function-space}
%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
%% % \end{align}
%% where the dual parameters $(\bm\alpha_n, \bm\beta_n)$ are vectors of,
%% \begin{align} \label{eq-gp-dual-params}
%%   \bm\alpha_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N} \qquad
%%   \bm\beta_{n} \coloneqq \left\{ \mathbb{E}_{p(f(\mathbf{x}_{i}) \mid \mathbf{y}_{n})} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \right\}_{i=1}^{N}
%% \end{align}
%% Importantly, this parameterisation
%% \textbf{dual-SVGP}
%% \begin{align} \label{eq-svgp-post}
%%   \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= \mu(\mathbf{x}_{*}) + \mathbf{k}_{\mathbf{z}*}^{T} \bm\alpha_{\mathbf{u}} \\
%%   \mathbb{V}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ f(\mathbf{x}_{*}) \right] &= k_{**} - \mathbf{k}_{\mathbf{z}*}^{T} \left[ \mathbf{K}_{\mathbf{z}\mathbf{z}}^{-1} - \left( \mathbf{K}_{\mathbf{z} \mathbf{z}} + \bm\beta_{\mathbf{u}} \right)^{-1} \right] \mathbf{k}_{\mathbf{z}*}
%% \end{align}
%% % \begin{align} \label{eq-laplace-approx-function-space}
%% %   \mathbb{E}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \\
%% %   \mathbb{V}_{p(f_{*} \mid \mathbf{y}_{n})} \left[ f_{*} \right] &= k_{**} - \mathbf{k}_{\mathbf{x}*}^{T} \bm\alpha_{n} \left( \mathbf{K}_{\mathbf{x} \mathbf{x}} + \diag(\bm\beta_{n})^{-1} \right)^{-1} \mathbf{k}_{\mathbf{x}*}
%% % \end{align}
%% where the dual parameters $(\bm\alpha_{\mathbf{u}}, \bm\beta_{\mathbf{u}})$ are vectors of,
%% \begin{align} \label{eq-svgp-dual-params}
%%   \bm\alpha_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \qquad
%%   \bm\beta_{\mathbf{u}} \coloneqq \mathbf{k}_{\mathbf{z}i} \mathbb{E}_{q_{\mathbf{u}}(f(\mathbf{x}_{i}))} \left[ \nabla^{2}_{f_{i}} \log p(y_{i} \mid f(\mathbf{x}_{i})) \right] \mathbf{k}_{\mathbf{z}i}^{T}
%% \end{align}
%% weight space posterior in \cref{eq-laplace-approx-weight-space} in
%% function space by linearising the BNN and interpreting it as a GP.
%% \begin{align} \label{eq-laplace-approx-function-space}
%%   \transitionFn_{\weights_{i}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
%% \end{align}
%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
%% \begin{align} \label{eq-laplace-approx-jacobian}
%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
%% \end{align}
%% % Note that the posterior in \cref{eq-laplace-approx-weight-space} is in weight space.
%% We can represent the weight space posterior in \cref{eq-laplace-approx-weight-space} in
%% function space by linearising the BNN and interpreting it as a GP.
%% \begin{align} \label{eq-laplace-approx-function-space}
%%   \transitionFn_{\weights_{i}^{*}}(\cdot) &\sim \mathcal{N} \left( \mu_{\weights_{i}^{*}}(\cdot), K_{\weights_{i}^{*}}(\cdot, \cdot') \right) \quad
%%   \mu_{\weights_{i}^{*}}(\cdot) &= \transitionFn_{\weights^{*}_{i}}(\cdot) \quad
%%   K_{\weights_{i}^{*}}(\cdot, \cdot') &= \mathbf{J}_{\weights^{*}_{i}}(\cdot) \bm\Sigma_{\weights^{*}_{i}} \mathbf{J}_{\weights^{*}_{i}}(\cdot')^{T}
%% \end{align}
%% where the Jacobian is given by $\mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}$.
%% \begin{align} \label{eq-laplace-approx-jacobian}
%% \mathbf{J}_{\weights^{*}_{i}}(\cdot) = \odv{\transitionFnWithParams(\cdot)}{\weights}_{\weights=\weights_{i}^{*}}
%% \end{align}
%\subsection{Fast Updates}
%Importantly, \cite{changFantasizingDualGPs2022} show that in the dual space,
%conditioning on new observations reduces to suming the dual variables from the previous time
%step with an update, given by,
%\todo{pick best way to show new data (using superscript new or just time indexing?)}
%\begin{align} \label{eq-dual-update-svgp}
%\dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
%\dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
%\end{align}
%Importantly, for a single new observation $((\state_{t}, \action_{t}), \state_{t+1})$ this update has
%complexity $\mathcal{O}(\numInducing^{2})$.
%This is a significant improvement to naive GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)^{3})$
%and sparse GP conditioning, which has complexity $\mathcal{O}((\numDataNew + \numDataOld)\numInducing^{2})$.
%\todo{double check these complexities are right and cite them/show equaitons}
%It is worth highlighting that the complexity of \cite{changFantasizingDualGPs2022} update does not increase during an episode.
%\subsubsection{Model-based RL}
%\subsubsection{Efficiently Sampling Functions for Posterior Sampling}
%\cite{wilsonEfficiently2020}
%\cite{wilsonPathwise2021}
%% \begin{align} \label{eq-dual-update-svgp}
%%  \dualParam{1}^{\text{new}} &\leftarrow \dualParam{1}^{\text{old}} +
%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
%%  \left[ \log p(\state_{t+1}^{\text{new}} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
%%  \dualParam{2}^{\text{new}} &\leftarrow \dualParam{2}^{\text{old}} +
%%   \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}))}
%%  \left[ \log p(\state_t^{\horizon+1} \mid \latentFn(\state_t^{\text{new}}, \action_t^{\text{new}}) ) \right] \\
%%  \dualParam{1}^{\horizon+1} &\leftarrow \dualParam{1}^{\horizon} +
%%   \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{\horizon}, \action_{\horizon}))}

>>>>

As demonstrated in \cite{adam2021dual}, the posterior under this model bears a structure akin to \cref{eq:gp_pred}. The authors of that paper see the significance of the dual variables for approximate inference, but write them using the natural parameterization, primarily because this form is more suitable for optimization through natural gradients. In order to link the dual variables defined in \cref{eq:dual_param}, we write them in the sparse GP using the dual variables
%
\begin{equation} \textstyle
  \valpha_{\vu}  =  \sum_{i=1}^N  \vkzi \, \hat{\alpha}_{i}
  \quad \text{and} \quad
  \MBeta_{\vu} =  \sum_{i=1}^N \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
\label{eq:dual_sparse}
\end{equation}
%
where the sparse dual variables are now a sum over \emph{all data points}, with $\valpha_{\vu} \in \R^{M}$ and $\MBeta_{\vu} \in \R^{M  \times M}$. Using this sparse definition of the dual variables, our sparse GP posterior takes the following form:
\begin{equation}\label{eq:dual_sparse_post}
   \myexpect_{q_{\vu}(\vf)}[f_i] = \vkzs^{\T} \MKzz^{-1} \valpha_{\vu}
   \quad \text{and} \quad 
   \textrm{Var}_{q_{\vu}(\vf)}[f_i]  = k_{ii} - \vkzs^\top [\MKzz^{-1} - (\MKzz + \MBeta_{\vu})^{-1} ]\vkzs
\end{equation}
where $\MKzz$ and $\vkzs$ are defined similarly to $\MKxx$ and $\vk_{\vx i}$ but over the inducing points $\{\vz_j\}_{i=1}^M$, $\vz \in \R^{D}$ \todo{These are already defined}, instead of the full data set $\dataset$. The key quantities we need to make predictions from our sparse GP from the converged neural network are $(\hat{\alpha}_i, \hat{\beta}_i)$ \cref{eq:dual_param_laplace} and a kernel function $\kappa$ . Contrasting \cref{eq:dual_sparse_post} and \cref{eq:gp_pred}, we can see that the computational complexity went from $\mathcal{O}(N^3)$ to $\mathcal{O}(M^3)$, with $M \ll N$.  Crucially, given the structure of our probabilistic model, our sparse dual variables \cref{eq:dual_sparse} are a compact representation of the full model projected using the kernel.

@@

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}..
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\MZ_t = \{\vz_i\}_{i=1}^M$ for task $t$ .\
%
We keep a memory buffer $\mathcal{M} = \{(\MZ_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\MZ_t$ are the inducing points selected from $\dataset_t$ and  $\vu_t = f_{\vw_t^*}(\MZ_t)\in \R^{M}$ are the neural network outputs associated to them, computed with the MAP estimate $\weights_t^*$ after task $t$. Note that, for notational convenience, we are extending our neural network notation to be compatible with multiple inputs points, \ie, each $i$\textsuperscript{th} entry is $f_{\weights_t^*}(\vz_i)\in \R$. Moreover, we restrict ourselves to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

@@
